---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/poissonconsulting/juggler.svg)](https://travis-ci.org/poissonconsulting/juggler)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/juggler?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/juggler)
[![codecov](https://codecov.io/gh/poissonconsulting/juggler/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/juggler)

# juggler

## Introduction

R package for simple checking, querying and modification
of JAGS model code.

All the functions take code for a single JAGS model in the form of string. If the 
model code is in the form of a character vector then the functions first collapse the 
vectors into a string using `paste0(x,sep="\n")`. They then strip comments.

The most useful function for most people is likely `jg_check()`. Run this on
JAGS model code to perform some basic checks such as balanced brackets
and valid block, distribution and function names. 

## Utilization

When presented with new code the first job is to use `jg_check` to see if the code has any problems.
Once checked code can be combined with code fragments using `jg_juggle` to
produce multiple models. 
If marked up using the MPAmpa syntax models can then be extended using
`jg_extend` to produce fast, flexible code.

```{r}
library(juggler)
x <- "data {
  Y2 <- Y * 2
}  
model {
  bIntercept ~ dnorm(0, 5^-2)
  bX ~ dnorm(0, 5^-2)
  sY ~ dunif(0, 5)

  for(i in 1:length(Y)) {
    mu[i] <- bIntercept + bX * X[i]
    Y2[i] ~ dnorm (mu[i], sY^-2)
  }
} "

jg_dists(x)
jg_funcs(x)
jg_vnodes(x)
jg_vnodes(x, indices = TRUE)
jg_vnodes(x, "stochastic", indices = TRUE)
jg_vnodes(x, "deterministic")
jg_block_names(x)
print(jg_check(x))
```

## Installation

To install from GitHub
```
# install.packages("devtools")
devtools::install_github("poissonconsulting/juggler")
```

## Inspiration

- [Nimble](http://r-nimble.org)
